\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2015-01-31 doc/flexiblesusy-paper.tex
adding self-energy symbol to be absolutely clear
describe symbol m_t to be absolutely clear
Note: The meaning of m_t was not obvious to Pietro Slavich, so, let's
be absolutely clear here.
add acknowledgments to DH

non-polarized part of the self-energy.  The separated QCD corrections

@@

  \Delta m_t^{(1),\text{qcd}} &= -\frac{g_3^2}{12 \pi^2} \left[5-3 \log\left(\frac{m_t^2}{\mu^2}\right)\right],\\

@@

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models and the GAMBIT
collaboration for helpful suggestions, particularly regarding
lowering our compiler prerequisites. The authors would also like to
thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Gregor Hellwig
for writing the first version of the E6SSM model file; Philip Diessner
for further adaptions to the E6SSM model file and for supplying it to
us and for for testing and identifying several bugs in \fs and in
SARAH, in work on the MRSSM; Ulrik Günther for compilation tests on
Mac OS X and Dylan Harries for spotting a bug in the configuration
script.
%
J.P. acknowledges support from the MEC and FEDER (EC) Grants
FPA2011--23596 and the Generalitat Valenciana under grant PROMETEOII/2013/017.
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.

>>>>

non-polarized part of the self-energy, $\Sigma_{t}$.  The separated QCD corrections

@@

  \Delta m_t^{(1),\text{qcd}} &= -\frac{g_3^2}{12 \pi^2} \left[5-3 \log\left(\frac{m_t^2}{\mu^2}\right)\right],
  \label{eq:top-selfenergy-qcd-1L}\\

@@

  \label{eq:top-selfenergy-qcd-2L}
In Eqs.\ \eqref{eq:top-selfenergy-qcd-1L} and
\eqref{eq:top-selfenergy-qcd-2L} $m_t$ denotes the \DRbar mass of the
top quark.

@@

A.V.\ would like to thank Florian Staub for countless explanations of
SARAH's internals, discussions, and exceptionally fast bug
fixing. P.A.~would like to thank Roman Nevzorov for useful discussions
about challenges in non-minimal SUSY models and the GAMBIT
collaboration for helpful suggestions, particularly regarding
lowering our compiler prerequisites. The authors would also like to
thank Lewis Tunstall for helping with early tests against
Next-to-Minimal Softsusy; Sophie Underwood for discovering problems
when introducing couplings with a single family index; Gregor Hellwig
for writing the first version of the E6SSM model file; Philip Diessner
for further adaptions to the E6SSM model file and for supplying it to
us and for for testing and identifying several bugs in \fs and in
SARAH, in work on the MRSSM; Ulrik Günther for compilation tests on
Mac OS X and Dylan Harries for spotting a bug in the configuration
script and creating an EWSB fixed-point iteration implementation for
the CNE$_6$SSM, which served as a prototype for implementing a
generalized EWSB fixed-point iteration.
%
J.P. acknowledges support from the MEC and FEDER (EC) Grants
FPA2011--23596 and the Generalitat Valenciana under grant PROMETEOII/2013/017.
This work has been supported by the German Research Foundation DFG
through Grant No.~STO876/2-1.
